Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal

### 2010-01-30 doc/msc-proposal/msc-snmp.tex
proposal: snmp operations

The common format of protocol data units is shown in Figure \ref{fig:snmp-pdu}. This format is used for all operations described in Section \ref{sec:opetations}, except for the GetBulk request. The PDU Type field has an integer value which identifies the type of the PDU. The Request Identifier is used to match requests with replies. It is generated by the device that sends a request and copied into this field in a response PDU by the responding SNMP entity. The Error Status tells the requesting SNMP entity the result of its request. A value of zero indicates that no error occurred; the other values indicate what sort of error happened. When Error Status is non-zero, the Error Index field points to the object generated the error, and has the value of zero in a request. The variable bindings is a set of name-value pairs identifying the MIB objects in the PDU, and in the case of messages other than requests, containing their values.
\begin{figure}[htp]	
\begin{center}
    \includegraphics[scale = 0.60]{img/snmp-pdu.pdf}
    \caption{SNMP Common PDU Format}   
	\label{fig:snmp-pdu}
\end{center}
\end{figure}

@@

The Get request is initiated by a manager. Upon receipt of the Get request, the agent processes each variable binding in the variable-binding list and produces a Response.

The Report protocol operation can be used internally to allow SNMP engines to communicate with each other for error notifications and clock synchronization.

>>>>

The common format of protocol data units is shown in Figure \ref{fig:snmp-pdu}. This format is used for all operations described in Section \ref{sec:opetations}, except for the GetBulk request. The PDU type field has an integer value which identifies the type of the PDU. The request identifier is used to match requests with replies. It is generated by the device that sends a request and copied into this field in a response PDU by the responding SNMP entity. The error status tells the requesting SNMP entity the result of its request. A value of zero indicates that no error occurred; the other values indicate what sort of error happened. When error status is non-zero, the error index field points to the object generated the error, and has the value of zero in a request. The variable bindings is a set of name-value pairs identifying the MIB objects in the PDU, and in the case of messages other than requests, containing their values.
\begin{figure}[htp]	
\begin{center}
    \includegraphics[scale = 0.60]{img/snmp-pdu.pdf}
    \caption{SNMP Common PDU Format}   
	\label{fig:snmp-pdu}
\end{center}
\end{figure}

@@

The Get request initiated by a manager allows to access and retrieve the value of one or more instances of management information. The agent processes each variable binding in the variable-binding list of the received Get PDU by resolving their values and produces a Response PDU. The response PDU is sent back to the manager. If the processing of any variable binding fails the details of the error are reflected in the the error status and error index fields in the Response PDU. The GetNext operation retrieves the value of the next existing MIB instances in lexicographic order. Successive GetNext operations can be used to walk the MIB instances without prior knowledge about the MIB structure. The GetBulk operation is a generalization of the GetNext operation where the agent performs a series of GetNext operations internally. This makes it easier to acquire large amounts of related information without initiating repeated GetNext operations. The manager can set values for the managed objects by using the Set operation.

The Trap is sent by an agent to a manager and indicates that an event has occurred or a certain condition is present. There is no confirmation associated with this notification delivery mechanism for this operation. The Inform operation provides a confirmed notification delivery mechanism. Finally, the Report operation can be used internally to allow SNMP engines to communicate with each other for error notifications and clock synchronization.
